---
title: "Plots"
author: "matishalin patel"
date: "28/07/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE) 
```
```{r, include=FALSE}
library(ggplot2)
library(tidyverse)
options(tidyverse.quiet = TRUE)
my_theme <- theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position="bottom"
  )
```


```{r, include=FALSE}
dat <- read_csv('../results/30082021_45.csv') %>% 
  filter(collapsed!=TRUE, err<=1E-6)
# %>%
#   filter(q==5, n==3)
```

## X and Y with Relatedness

```{r , include=FALSE}
plotDat <- dat %>% filter(n==3&q==5, epsilon==1, stab==5) %>% 
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed) %>%
  summarise(
    Cooperation = mean(indAvgX, na.rm=T),
    Conflict = mean(indAvgY, na.rm=T),
    Relatedness = mean(avgR, na.rm=T),
    Harshness = as.factor(1-ratio)
  ) %>%
  gather("Trait", "Investment", 
         Cooperation, Conflict) %>%
  filter(
         # epsilon%in%c(1,5,10),
         ratio%in%c(0.1, 0.5, 0.9),
         # stab%in%c(5, 10, 15)
         ) %>%
  ungroup()
```
```{r}
ggplot(plotDat %>% filter(force==0.03)) +
  facet_wrap(~Trait, scales="free") +
  geom_path(aes(Relatedness, 
                Investment, 
                linetype=Harshness), size=1) +
  my_theme
ggsave("../paper/graphs/traits_with_R.pdf");
```

## X and Y with Encounter Rate

```{r, include=FALSE}
plotDat <- dat %>% filter(n==3&q==5, d==0.3, stab==10) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(force, ratio, epsilon, fixed) %>%
  summarise(
    Cooperation = mean(indAvgX, na.rm=T),
    Conflict = mean(indAvgY, na.rm=T),
    EncounterRate = log2(epsilon),
    Harshness = as.factor(1-ratio)
  ) %>%
  gather("Trait", "Investment", 
         Cooperation, Conflict) %>%
  filter(
         # epsilon%in%c(1,5,10),
         # ratio%in%c(0.1, 0,45, 0.5, 0.55, 0.9),
         # stab%in%c(5, 10, 15)
         ) %>%
  ungroup()
```
```{r}
ggplot(plotDat %>% filter(force==0.03)) +
  facet_wrap(~Trait, scales="free") +
  geom_path(aes(EncounterRate, 
                Investment, 
                linetype=Harshness), size=1) +
  my_theme
```

## Relatedness and Mortality 
```{r, include=FALSE}
plotDat <- dat %>% filter(n==3&q==5, epsilon==1) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed) %>%
  summarise(
    Mortality = mean(avgMort, na.rm=T),
    Relatedness = mean(avgR, na.rm=T),
    Harshness = as.factor(1-ratio)
  ) %>%
  filter(
         # epsilon%in%c(1,5,10),
         ratio%in%c(0.1, 0.5, 0.9),
         # stab%in%c(5, 10, 15)
         ) %>%
  ungroup()
```
```{r}
ggplot(plotDat %>% filter(force==0.03)) +
  # facet_wrap(~d)+
  geom_path(aes(Relatedness, 
                Mortality, 
                linetype=Harshness), size=1) +
  my_theme
```

## Effect of Quality level on traits

```{r}
td <- dat %>% 
  filter(q==5, n==3, force==0.03) %>%
  # filter(q==5, n==3, epsilon%in%c(5,10),d==0.5, ratio==0.5, stab==10, force==0.03) %>%
  pivot_longer(
    cols = matches("(t[XYF])(\\d)(\\d\\b)"),
    names_to = c("Trait", "Quality", "Size"),
    names_pattern = "(t[XYF])(\\d)(\\d\\b)",
    values_to = "Investment"
  ) %>% filter(!is.na(Investment), Size>0) %>%
  select(Trait, Investment, Quality, Size, d, epsilon, ratio, stab) %>%
  pivot_wider(names_from = Trait, values_from=Investment) %>%
  mutate(
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  group_by(d, epsilon, ratio, stab) %>%
  mutate(
    normF = tF/(sum(tF)),
    reg = normF*Size,
    tXi = (tX * reg) / sum(reg),
    tYi = (tY * reg) / sum(reg)
  )
  
```
```{r}
plotDat <- td %>% filter(d==0.5, epsilon==1, stab==5) %>%
  pivot_longer(
    cols=all_of(c("tX", "tY")),
    names_to = "Trait",
    values_to = "Investment"
  ) %>%
  mutate(
         Harshness = as.factor(1-ratio)
  ) %>%
  filter( 
         Harshness%in%c(0.1,0.4, 0.5,0.6, 0.9),
         # stab%in%c(5, 10, 15),
         Size==3
  ) %>% 
  ungroup()
  
plotDat$Trait <- recode_factor(plotDat$Trait,
                        tX="Cooperation", 
                        tY="Conflict")
```
```{r}
ggplot(filter(plotDat, Trait=="Cooperation")) + 
  facet_grid(~Trait, scales="free_y") +
  geom_line(aes(Quality, Investment, 
                linetype=as.factor(Harshness)),
            size=1) +
  my_theme
ggplot(filter(plotDat, Trait=="Conflict")) + 
  facet_grid(~Trait, scales="free_y") +
  geom_line(aes(Quality, Investment, 
                linetype=as.factor(Harshness)),
            size=1) +
  my_theme
```

## Effect of Size level on traits
```{r}
td <- dat %>% 
  # filter(q==3, n==5, force==0.03) %>% distinct() %>%
  filter(q==3, n==5, epsilon%in%c(2), force==0.03) %>%
  pivot_longer(
    cols = matches("(t[XYF])(\\d)(\\d\\b)"),
    names_to = c("Trait", "Quality", "Size"),
    names_pattern = "(t[XYF])(\\d)(\\d\\b)",
    values_to = "Investment"
  ) %>% filter(!is.na(Investment), Size>0) %>%
  select(Trait, Investment, Quality, Size, d, epsilon, ratio, stab) %>%
  pivot_wider(names_from = Trait, values_from=Investment) %>%
  mutate(
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  group_by(d, epsilon, ratio, stab) %>%
  mutate(
    normF = tF/(sum(tF)),
    reg = normF*Size,
    tXi = (tX * reg) / sum(reg),
    tYi = (tY * reg) / sum(reg)
  )
  
```
```{r}
plotDat <- td %>% filter(d==0.5, epsilon==2, stab==10) %>%
  pivot_longer(
    cols=all_of(c("tX", "tY")),
    names_to = "Trait",
    values_to = "Investment"
  ) %>%
  mutate(
         Harshness = as.factor(1-ratio)
  ) %>%
  filter( 
         # Harshness%in%c(0.1, 0.5, 0.9),
         # stab%in%c(5, 10, 15),
         Size>1
  ) %>% 
  ungroup()
  
plotDat$Trait <- recode_factor(plotDat$Trait,
                        tX="Cooperation", 
                        tY="Conflict")
```
```{r}
ggplot(plotDat%>%filter(Harshness==0.5)) + 
  facet_wrap(~Trait, scales="free_y") +
  geom_line(aes(Size, Investment*Size, 
                linetype=as.factor(Quality)),
            size=1) +
  my_theme
```

## Effect of Harshness on Traits 

```{r , include=FALSE}
plotDat <- dat %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  filter(q==5, n==3) %>%
  group_by(d, force, ratio, epsilon, fixed, stab) %>%
  summarise(
    Cooperation = mean(groupAvgX, na.rm=T),
    Conflict = mean(indAvgY, na.rm=T),
    Harshness = as.numeric(1-ratio),
    Dispersal = as.factor(d)
  ) %>%
  gather("Trait", "Investment", 
         Cooperation, Conflict) %>%
  filter(
         epsilon%in%c(0.125,0.5,1),
         d%in%c(0.1, 0.5, 0.9),
         # Harshness%in%c(0.1, 0.2, 0.3, 0.4 ,0.5,
                        # 0.6, 0.7, 0.8,0.9)
         ) %>%
  ungroup()
```
```{r }
ggplot(plotDat %>% 
         filter(force==0.03,  epsilon==1, stab==10)) +
  facet_wrap(~Trait, scales="free") +
  geom_path(aes(Harshness, 
                Investment, linetype=as.factor(d)), size=1) +
  my_theme

ggplot(plotDat %>%
         filter(force==0.03,  d==0.5, stab==10)) +
  facet_wrap(~Trait, scales="free") +
  geom_path(aes(Harshness,
                Investment, linetype=as.factor(epsilon)), size=1) +
  my_theme
```

## Effect of Stability on Traits 

```{r , include=FALSE}
plotDat <- dat %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, stab, fixed, epsilon, ratio) %>%
  summarise(
    Cooperation = mean(indAvgX, na.rm=T),
    Conflict = mean(indAvgY, na.rm=T),
    Stability = as.numeric(stab),
    Dispersal = as.factor(d)
  ) %>%
  gather("Trait", "Investment", 
         Cooperation, Conflict) %>%
  filter(
         # epsilon%in%c(1,5,10),
         d%in%c(0.1, 0.5, 0.9),
         # stab%in%c(5, 10, 15)
         ) %>%
  ungroup()
```
```{r }
ggplot(plotDat %>% filter(force==0.03, ratio==0.5, epsilon==2)) +
  facet_wrap(~Trait, scales="free") +
  geom_path(aes(Stability, 
                Investment, 
                linetype=Dispersal), size=1) +
  my_theme
```

## Effect of Harshness on Resource Value
```{r , include=FALSE}
plotDat <- dat %>%
  filter(q==5&n==3, d==0.5, force==0.03, stab==5) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed, stab, epsilon) %>%
  summarise(
    Value = mean(qVal, na.rm=T),
    Harshness = as.numeric(1-ratio),
    Dispersal = as.factor(d)
  ) %>%
  # filter(
  #        # epsilon%in%c(1,5,10),
  #        d%in%c(0.1, 0.5, 0.9),
  #        # stab%in%c(5, 10, 15)
  #        ) %>%
  ungroup()
```
```{r }
ggplot(plotDat) +
  geom_path(aes(Harshness, 
                Value, 
                linetype=as.factor(epsilon)), size=1) +
  my_theme
```

## Effect of EncounterRate on Resource Value
```{r , include=FALSE}
plotDat <- dat %>%
  filter(q==5&n==3, ratio==0.5, force==0.03, stab==5) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed, stab, epsilon) %>%
  summarise(
    Value = mean(qVal, na.rm=T),
    Harshness = as.numeric(1-ratio),
    Dispersal = as.factor(d)
  ) %>%
  # filter(
  #        # epsilon%in%c(1,5,10),
  #        d%in%c(0.1, 0.5, 0.9),
  #        # stab%in%c(5, 10, 15)
  #        ) %>%
  ungroup()
```
```{r }
ggplot(plotDat%>%filter(Harshness==0.5)) +
  geom_path(aes(log2(epsilon), 
                Value, linetype=Dispersal), size=1) +
  my_theme
```





## Effect of Harshness on Productivity
# ```{r , include=FALSE}
# plotDat <- td %>%
#   # filter(force==0|(force!=0&err<1E-6)) %>%
#   group_by(d, force, ratio, fixed) %>%
#   summarise(
#     Value = mean(Pfi, na.rm=T),
#     Harshness = as.numeric(1-ratio),
#     Dispersal = as.factor(d)
#   ) %>%
#   filter(
#          # epsilon%in%c(1,5,10),
#          d%in%c(0.1, 0.5, 0.9),
#          # stab%in%c(5, 10, 15)
#          ) %>%
#   ungroup()
# ```
# ```{r }
# ggplot(plotDat %>% filter(force==0.03)) +
#   geom_path(aes(Harshness, 
#                 Value, 
#                 linetype=Dispersal), size=1) +
#   my_theme
# ```

## Effect of Quality and Size on traits by ratio Contour Plots

```{r}
td <- dat %>% 
  filter(q==5, n==3, force==0.03) %>%
  # filter(q==5, n==3, epsilon%in%c(5,10),d==0.5, ratio==0.5, stab==10, force==0.03) %>%
  pivot_longer(
    cols = matches("(t[XYF])(\\d)(\\d\\b)"),
    names_to = c("Trait", "Quality", "Size"),
    names_pattern = "(t[XYF])(\\d)(\\d\\b)",
    values_to = "Investment"
  ) %>% filter(!is.na(Investment), Size>0) %>%
  select(Trait, Investment, Quality, Size, d, epsilon, ratio, stab) %>%
  pivot_wider(names_from = Trait, values_from=Investment) %>%
  mutate(
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  group_by(d, epsilon, ratio, stab) %>%
  mutate(
    normF = tF/(sum(tF)),
    reg = normF*Size,
    tXi = (tX * reg) / sum(reg),
    tYi = (tY * reg) / sum(reg),
    tXn = (tX-mean(tX))/sd(tX),
    tYn = (tY-mean(tY))/sd(tY)
  )
  
```
```{r}
plotDat <- td %>% filter(d==0.5, epsilon==1, stab==5) %>%
  pivot_longer(
    cols=all_of(c("tXn", "tYn")),
    names_to = "Trait",
    values_to = "Investment"
  ) %>%
  mutate(
         Harshness = as.factor(1-ratio)
  ) %>%
  filter( 
         # Harshness%in%c(0.1, 0.4, 0.5, 0.6, 0.9),
         # stab%in%c(5, 10, 15),
         # Size>0
  ) %>% 
  ungroup()
  
plotDat$Trait <- recode_factor(plotDat$Trait,
                        tXn="Cooperation", 
                        tYn="Conflict")
```
```{r, fig.width=7,fig.height=10}
ggplot(plotDat%>%filter(Size==3)) + 
  facet_grid(rows=vars(Trait), scales="free") +
  geom_tile(aes(reorder(Harshness, desc(Harshness)), Quality, fill=Investment)) +
  scale_fill_viridis_c() +
  my_theme
```


```{r}
td <- dat %>% 
  filter(q==3, n==5, force==0.03) %>%
  # filter(q==5, n==3, epsilon%in%c(5,10),d==0.5, ratio==0.5, stab==10, force==0.03) %>%
  pivot_longer(
    cols = matches("(t[XYF])(\\d)(\\d\\b)"),
    names_to = c("Trait", "Quality", "Size"),
    names_pattern = "(t[XYF])(\\d)(\\d\\b)",
    values_to = "Investment"
  ) %>% filter(!is.na(Investment), Size>0) %>%
  select(Trait, Investment, Quality, Size, d, epsilon, ratio, stab) %>%
  pivot_wider(names_from = Trait, values_from=Investment) %>%
  mutate(
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  group_by(d, epsilon, ratio, stab) %>%
  mutate(
    normF = tF/(sum(tF)),
    reg = normF*Size,
    tXi = (tX * reg) / sum(reg),
    tYi = (tY * reg) / sum(reg),
    tXn = (tX-mean(tX))/sd(tX),
    tYn = (tY-mean(tY))/sd(tY)
  )
  
```
```{r}
plotDat <- td %>% filter(d==0.5, epsilon==1, stab==5) %>%
  pivot_longer(
    cols=all_of(c("tXn", "tYn")),
    names_to = "Trait",
    values_to = "Investment"
  ) %>%
  mutate(
         Harshness = factor(1-ratio)
  ) %>%
  filter( 
         # Harshness%in%c(0.1, 0.4, 0.5, 0.6, 0.9),
         # stab%in%c(5, 10, 15),
         Size>1
  ) %>% 
  ungroup()
  
plotDat$Trait <- recode_factor(plotDat$Trait,
                        tXn="Cooperation", 
                        tYn="Conflict")
```
```{r, fig.width=7,fig.height=10}
ggplot(plotDat%>%filter(Quality==3)) + 
  facet_grid(rows=vars(Trait), scales="free") +
  geom_tile(aes(reorder(Harshness, desc(Harshness)), Size, fill=Investment)) +
  scale_fill_viridis_c() +
  my_theme
```

## Peturb graphs
```{r}
td <- dat %>% 
  filter(q==3, n==5, d==0.5, epsilon==2, d==0.5, 
         stab==10, force==0.03) %>%
  pivot_longer(
    cols = matches("((?:rF_0_\\d+)|(?:t[XY]))(\\d)(\\d)"),
    names_to = c("Measure", "Quality", "Size"),
    names_pattern = "((?:rF_0_\\d+)|(?:t[XY]))(\\d)(\\d)",
    values_to = "Value"
  ) %>%
  filter(!is.na(Value)) %>%
  pivot_wider(
    names_from = Measure, values_from = Value
  ) %>%
  pivot_longer(
    cols = matches("(rF)_(0_\\d+)"),
    names_to = c("freq", "pRatio"),
    names_pattern = "(rF)_(0_\\d+)",
    values_to = "pFreq"
  ) %>%
  # filter(q==5, n==3, epsilon%in%c(5,10),d==0.5, ratio==0.5, stab==10, force==0.03) %>%
  # pivot_longer(
  #   cols = matches("(rF)_(0_\\d+)(\\d)(\\d)"),
  #   names_to = c("Measure", "pRatio", "Quality", "Size"),
  #   names_pattern = "(rF)_(0_\\d+)(\\d)(\\d)",
  #   values_to = "pFreq"
  # ) %>%
  # pivot_longer(
  #   cols = matches("(t[XY])(\\d)(\\d\\b)"),
  #   names_to = c("Trait", "Quality2", "Size2"),
  #   names_pattern = "(t[XY])(\\d)(\\d\\b)",
  #   values_to = "Investment"
  # ) %>%
  mutate(
    pRatio = as.numeric(str_replace(pRatio, "_", ".")),
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  filter(ratio%in%unique(pRatio)) %>%
  select(q, n, d, epsilon, stab, force, 
         freq, tX, tY, Quality, Size, pRatio, pFreq, ratio) %>%
  group_by(epsilon, stab, d, pRatio, ratio) %>%
  filter(Size>1) %>%
  mutate(normF = pFreq/sum(pFreq)) %>%
  summarize(
    pcX = sum(tX*normF*Size) / sum(Size*normF),
    pcY = sum(tY*normF*Size) / sum(Size*normF)
    # pcX = mean(tX*normF),
    # pcY = mean(tX*normF)
    ) %>%
  ungroup() %>%
  group_by(ratio, d, epsilon, stab) %>%
  mutate(
    baseX = pcX[pRatio == ratio],
    baseY = pcY[pRatio == ratio],
    diffX = pcX - baseX,
    diffY = pcY - baseY,
    Harshness = as.numeric(1-ratio),
    pHarsh = as.numeric(1-pRatio)
  )
```

```{r}
ggplot(td) + 
  geom_line(aes(pHarsh, diffX, colour=as.factor(Harshness))) +
  geom_hline(yintercept=0) +
  geom_point(aes(Harshness, rep(0,length(Harshness)), colour=as.factor(Harshness))) +
  my_theme
```

```{r}
ggplot(td) + 
  geom_line(aes(pHarsh, diffY, colour=as.factor(Harshness))) +
  geom_hline(yintercept=0) +
  geom_point(aes(Harshness, rep(0,length(Harshness)), colour=as.factor(Harshness))) +
  my_theme
```

## Fight number 
# Effect of Encounter rate on number of fights
```{r , include=FALSE}
plotDat <- dat %>%
  filter(q==5&n==3, ratio==0.5, force==0.03, stab==5) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed, stab, epsilon) %>%
  summarise(
    Value = mean(fightnum, na.rm=T),
    Harshness = as.numeric(1-ratio),
    Dispersal = as.factor(d)
  ) %>%
  # filter(
  #        # epsilon%in%c(1,5,10),
  #        d%in%c(0.1, 0.5, 0.9),
  #        # stab%in%c(5, 10, 15)
  #        ) %>%
  ungroup()
```
```{r }
ggplot(plotDat%>%filter(Harshness==0.5)) +
  geom_path(aes((epsilon), 
                Value, linetype=Dispersal), size=1) +
  my_theme
```

# Effect of Harshness on number of fights
```{r , include=FALSE}
plotDat <- dat %>%
  filter(q==5&n==3, d==0.5, force==0.03, stab==5) %>%
  # filter(force==0|(force!=0&err<1E-6)) %>%
  group_by(d, force, ratio, fixed, stab, epsilon) %>%
  summarise(
    Value = mean(fightnum, na.rm=T),
    Harshness = as.numeric(1-ratio),
    Dispersal = as.factor(d)
  ) %>%
  filter(
    epsilon%in%c(0.125, 0.5, 1, 2,4),
  #        d%in%c(0.1, 0.5, 0.9),
  #        # stab%in%c(5, 10, 15)
         ) %>%
  ungroup()
```
```{r }
ggplot(plotDat) +
  geom_path(aes(Harshness, 
                Value, linetype=as.factor(epsilon)), size=1) +
  my_theme
ggsave("../graphs/fights.pdf");
```

## Effect of Quality level on tFreq

```{r}
td <- dat %>% 
  filter(q==5, n==3, force==0.03) %>%
  # filter(q==5, n==3, epsilon%in%c(2),d==0.5, ratio==0.5, stab==10, force==0.03) %>%
  pivot_longer(
    cols = matches("(t[XYF])(\\d)(\\d\\b)"),
    names_to = c("Trait", "Quality", "Size"),
    names_pattern = "(t[XYF])(\\d)(\\d\\b)",
    values_to = "Investment"
  ) %>% filter(!is.na(Investment), Size>1) %>%
  select(Trait, Investment, Quality, Size, d, epsilon, ratio, stab) %>%
  pivot_wider(names_from = Trait, values_from=Investment) %>%
  mutate(
    Size = as.numeric(Size),
    Quality = as.numeric(Quality)
  ) %>%
  group_by(d, epsilon, ratio, stab, Quality) %>%
  summarize(
    freq = sum(tF)
  )
  
```
```{r}
plotDat <- td %>% filter(d==0.5, epsilon==1, stab==5) %>%
  mutate(
         Harshness = 1-ratio
  ) %>%
  filter(
    Harshness<0.11||Harshness%in%c(0.5, 0.9)
  ) %>%
  ungroup()
```
```{r}
ggplot(plotDat) + 
  # facet_grid(~Harshness, scales="free_y") +
  geom_line(aes(Quality, freq, colour=as.factor(Harshness)),
            size=1) +
  my_theme
ggsave("../graphs/wealth_dist.pdf");
```

```{r}
plotDat <- td %>% filter(d==0.5, ratio%in%c(0.4, 0.45,0.5,0.55, 0.6), stab==5) %>%
  mutate(
         Harshness = 1-ratio
  ) %>%
  ungroup()
```
```{r, fig.width=8,fig.height=20}
ggplot(plotDat) + 
  facet_grid(rows=vars(Harshness), scales="free_y") +
  geom_line(aes(Quality, freq, colour=as.factor(epsilon)),
            size=1) +
  my_theme
```